\pkg{RProtoBuf}: Efficient Cross-Language Data Serialization in \proglang{R}

### 2014-01-26 papers/jss/article.Rnw
one spell checks, lots of 'data set' instead of dataset, one 'work flow'
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/rprotobuf@855 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

Modern data collection and analysis pipelines increasingly involve collections
of decoupled components in order to better manage software complexity 
through reusability, modularity, and fault isolation \citep{Wegiel:2010:CTT:1932682.1869479}.
These pipelines are frequently built using different programming 
languages for the different phases of data analysis -- collection,
cleaning, modeling, analysis, post-processing, and
presentation -- in order to take advantage of the unique combination of
performance, speed of development, and library support offered by
different environments and languages.  Each stage of such a data
analysis pipeline may produce intermediate results that need to be
stored in a file, or sent over the network for further processing.

@@

Data analysts and researchers often use character-separated text formats such
as \texttt{CSV} \citep{shafranovich2005common} to export and import
data. However, anyone who has ever used \texttt{CSV} files will have noticed
that this method has many limitations: it is restricted to tabular data,
lacks type-safety, and has limited precision for numeric values.  Moreover,
ambiguities in the format itself frequently cause problems.  For example,
conventions on which characters is used as separator or decimal point vary by
country.  \emph{Extensible Markup Language} (\texttt{XML}) is another
well-established and widely-supported format with the ability to define just
about any arbitrarily complex schema \citep{nolan2013xml}. However, it pays
for this complexity with comparatively large and verbose messages, and added
complexity at the parsing side (which are somewhat mitigated by the
availability of mature libraries and parsers). Because \texttt{XML} is 
text-based and has no native notion of numeric types or arrays, it usually not a
very practical format to store numeric datasets as they appear in statistical
applications.

@@

This paper describes an \proglang{R} interface to Protocol Buffers,
and is organized as follows. Section~\ref{sec:protobuf}
provides a general high-level overview of Protocol Buffers as well as a basic
motivation for their use.
Section~\ref{sec:rprotobuf-basic} describes the interactive \proglang{R} interface
provided by the \CRANpkg{RProtoBuf} package, and introduces the two main abstractions:
\emph{Messages} and \emph{Descriptors}.  Section~\ref{sec:rprotobuf-classes}
details the implementation details of the main S4 classes and methods.  
Section~\ref{sec:types} describes the challenges of type coercion
between \proglang{R} and other languages.  Section~\ref{sec:evaluation} introduces a
general \proglang{R} language schema for serializing arbitrary \proglang{R} objects and evaluates
it against the serialization capbilities built directly into \proglang{R}.  Sections~\ref{sec:mapreduce}
and \ref{sec:opencpu} provide real-world use cases of \CRANpkg{RProtoBuf}
in MapReduce and web service environments, respectively, before
Section~\ref{sec:summary} concludes.

@@

\begin{itemize}
\item \emph{Portable}:  Enable users to send and receive data between
  applications as well as different computers or operating systems.
\item \emph{Efficient}:  Data is serialized into a compact binary
  representation for transmission or storage.
\item \emph{Extensible}:  New fields can be added to Protocol Buffer Schemas
  in a forward-compatible way that does not break older applications.
\item \emph{Stable}:  Protocol Buffers have been in wide use for over a
  decade.
\end{itemize}

@@

Figure~\ref{fig:protobuf-distributed-usecase} illustrates an example
communication workflow with Protocol Buffers and an interactive \proglang{R} session.
Common use cases include populating a request remote-procedure call (RPC)
Protocol Buffer in \proglang{R} that is then serialized and sent over the network to a
remote server.  The server would then deserialize the message, act on the
request, and respond with a new Protocol Buffer over the network. 
The key difference to, say, a request to an \pkg{Rserve} instance is that
the remote server may be implemented in any language, with no
dependence on \proglang{R}.

@@

To illustrate how this method works, we attempt to convert all of the built-in 
datasets from \proglang{R} into this serialized Protocol Buffer representation.

@@

There are \Sexpr{n} standard data sets included in the base-r \pkg{datasets}
package. These datasets include data frames, matrices, time series, tables lists,
and some more exotic data classes. The \texttt{can\_serialize\_pb} method is 
used to determine which of those can fully be converted to the \texttt{rexp.proto}
Protocol Buffer representation. This method simply checks if any of the values or
attributes in an object is of an unsupported type:

@@

\Sexpr{m} data sets can be converted to Protocol Buffers
without loss of information (\Sexpr{format(100*m/n,digits=1)}\%). Upon closer
inspection, all other datasets are objects of class \texttt{nfnGroupedData}.
This class represents a special type of data frame that has some additional 
attributes (such as a \emph{formula} object) used by the \pkg{nlme} package.
Because formulas are \proglang{R} \emph{language} objects, they have little meaning to
other systems, and are not supported by the \texttt{rexp.proto} descriptor.
When \texttt{serialize\_pb} is used on objects of this class, it will serialize
the data frame and all attributes, except for the formula.

@@

Table~\ref{tab:compression} shows the sizes of 50 sample \proglang{R} datasets as
returned by object.size() compared to the serialized sizes.
%The summary compression sizes are listed below, and a full table for a
%sample of 50 datasets is included on the next page.  
Note that Protocol Buffer serialization results in slightly
smaller byte streams compared to native \proglang{R} serialization in most cases,
but this difference disappears if the results are compressed with gzip.
%Sizes are comparable but Protocol Buffers provide simple getters and setters
%in multiple languages instead of requiring other programs to parse the \proglang{R}
%serialization format. % \citep{serialization}.
One takeaway from this table is that the universal \proglang{R} object schema
included in \CRANpkg{RProtoBuf} does not in general provide
any significant saving in file size compared to the normal serialization
mechanism in \proglang{R}.
% redundant: which is seen as equally compact.
The benefits of \CRANpkg{RProtoBuf} accrue more naturally in applications where
multiple programming languages are involved, or when a more concise
application-specific schema has been defined.  The example in the next
section satisfies both of these conditions.

% latex table generated in \proglang{R} 3.0.2 by xtable 1.7-0 package
% Fri Dec 27 17:00:03 2013
\begin{table}[h!]
\begin{center}
  \small
\scalebox{0.9}{
\begin{tabular}{lrrrrr}
  \toprule
  Data Set & object.size & \multicolumn{2}{c}{\proglang{R} Serialization} &
  \multicolumn{2}{c}{RProtoBuf Serial.} \\
  & & default & gzipped & default & gzipped \\
  \cmidrule(r){2-6}
  uspop & 584 & 268 & 172 & 211 & 148 \\
  Titanic & 1960 & 633 & 257 & 481 & 249 \\
  volcano & 42656 & 42517 & 5226 & 42476 & 4232 \\
  euro.cross & 2728 & 1319 & 910 & 1207 & 891 \\
  attenu & 14568 & 8234 & 2165 & 7771 & 2336 \\
  ToothGrowth & 2568 & 1486 & 349 & 1239 & 391 \\
  lynx & 1344 & 1028 & 429 & 971 & 404 \\
  nottem & 2352 & 2036 & 627 & 1979 & 641 \\
  sleep & 2752 & 746 & 282 & 483 & 260 \\
  co2 & 4176 & 3860 & 1473 & 3803 & 1453 \\
  austres & 1144 & 828 & 439 & 771 & 410 \\
  ability.cov & 1944 & 716 & 357 & 589 & 341 \\
  EuStockMarkets & 60664 & 59785 & 21232 & 59674 & 19882 \\
  treering & 64272 & 63956 & 17647 & 63900 & 17758 \\
  freeny.x & 1944 & 1445 & 1311 & 1372 & 1289 \\
  Puromycin & 2088 & 813 & 306 & 620 & 320 \\
  warpbreaks & 2768 & 1231 & 310 & 811 & 343 \\
  BOD & 1088 & 334 & 182 & 226 & 168 \\
  sunspots & 22992 & 22676 & 6482 & 22620 & 6742 \\
  beaver2 & 4184 & 3423 & 751 & 3468 & 840 \\
  anscombe & 2424 & 991 & 375 & 884 & 352 \\
  esoph & 5624 & 3111 & 548 & 2240 & 665 \\
  PlantGrowth & 1680 & 646 & 303 & 459 & 314 \\
  infert & 15848 & 14328 & 1172 & 13197 & 1404 \\
  BJsales & 1632 & 1316 & 496 & 1259 & 465 \\
  stackloss & 1688 & 917 & 293 & 844 & 283 \\
  crimtab & 7936 & 4641 & 713 & 1655 & 576 \\
  LifeCycleSavings & 6048 & 3014 & 1420 & 2825 & 1407 \\
  Harman74.cor & 9144 & 6056 & 2045 & 5861 & 2070 \\
  nhtemp & 912 & 596 & 240 & 539 & 223 \\
  faithful & 5136 & 4543 & 1339 & 4936 & 1776 \\
  freeny & 5296 & 2465 & 1518 & 2271 & 1507 \\
  discoveries & 1232 & 916 & 199 & 859 & 180 \\
  state.x77 & 7168 & 4251 & 1754 & 4068 & 1756 \\
  pressure & 1096 & 498 & 277 & 427 & 273 \\
  fdeaths & 1008 & 692 & 291 & 635 & 272 \\
  euro & 976 & 264 & 186 & 202 & 161 \\
  LakeHuron & 1216 & 900 & 420 & 843 & 404 \\
  mtcars & 6736 & 3798 & 1204 & 3633 & 1206 \\
  precip & 4992 & 1793 & 813 & 1615 & 815 \\
  state.area & 440 & 422 & 246 & 405 & 235 \\
  attitude & 3024 & 1990 & 544 & 1920 & 561 \\
  randu & 10496 & 9794 & 8859 & 10441 & 9558 \\
  state.name & 3088 & 844 & 408 & 724 & 415 \\
  airquality & 5496 & 4551 & 1241 & 2874 & 1294 \\
  airmiles & 624 & 308 & 170 & 251 & 148 \\
  quakes & 33112 & 32246 & 9898 & 29063 & 11595 \\
  islands & 3496 & 1232 & 563 & 1098 & 561 \\
  OrchardSprays & 3600 & 2164 & 445 & 1897 & 483 \\
  WWWusage & 1232 & 916 & 274 & 859 & 251 \\
  \bottomrule
%  Total & 391176 & 327537 & 99161 & 313456 & 100308 \\
  Relative Size & 100\% & 83.7\% & 25.3\% & 80.1\% & 25.6\%\\
  \bottomrule
\end{tabular}
}
\caption{Serialization sizes for default serialization in \proglang{R} and
  \CRANpkg{RProtoBuf} for 50 \proglang{R} datasets.}
\label{tab:compression}
\end{center}
\end{table}

@@

The \texttt{HTTP GET} method is used to read a resource from OpenCPU. For example,
to access the dataset \texttt{Animals} from the package \texttt{MASS}, a 
client performs the following HTTP request:

@@

Because both HTTP and Protocol Buffers have libraries available for many 
languages, clients can be implemented in just a few lines of code. Below
is example code for both \proglang{R} and Python that retrieves a dataset from \proglang{R} with 
OpenCPU using a protobuf message. In \proglang{R}, we use the HTTP client from 
the \texttt{httr} package \citep{httr}. In this example we
download a dataset which is part of the base \proglang{R} distribution, so we can
verify that the object was transferred without loss of information.

@@

This code suggests a method for exchanging objects between \proglang{R} servers, however this might as 
well be done without Protocol Buffers. The main advantage of using an inter-operable format 
is that we can actually access \proglang{R} objects from within another
programming language. For example, in a very similar fashion we can retrieve the same
dataset in a Python client. To parse messages in Python, we first compile the 
\texttt{rexp.proto} descriptor into a python module using the \texttt{protoc} compiler:

@@

# Parse rexp.proto message
msg = REXP()
msg.ParseFromString(res.read())
print(msg)
\end{verbatim}
The \texttt{msg} object contains all data from the Animals dataset. From here we
can easily extract the desired fields for further use in Python.

@@

\section{Summary}  
\label{sec:summary}
Over the past decade, many formats for interoperable
data exchange have become available, each with their unique features,
strengths and weaknesses.  
Text based formats such as \texttt{CSV} and \texttt{JSON} are easy to use, and will likely 
remain popular among statisticians for many years to come. However, in the 
context of increasingly complex analysis stacks and applications involving 
distributed computing as well as mixed language analysis pipelines, choosing a more 
sophisticated data interchange format may reap considerable benefits. 
%Protocol Buffers is itself not a protocol.
%Forward-compatibility is one of the features. No need to re-iterate those 
The Protocol Buffers standard and library offer a unique combination of features, 
performance, and maturity, that seems particulary well suited for data-driven 
applications and numerical computing.

>>>>

Modern data collection and analysis pipelines increasingly involve collections
of decoupled components in order to better manage software complexity 
through reusability, modularity, and fault isolation \citep{Wegiel:2010:CTT:1932682.1869479}.
These pipelines are frequently built using different programming 
languages for the different phases of data analysis --- collection,
cleaning, modeling, analysis, post-processing, and
presentation --- in order to take advantage of the unique combination of
performance, speed of development, and library support offered by
different environments and languages.  Each stage of such a data
analysis pipeline may produce intermediate results that need to be
stored in a file, or sent over the network for further processing.

@@

Data analysts and researchers often use character-separated text formats such
as \texttt{CSV} \citep{shafranovich2005common} to export and import
data. However, anyone who has ever used \texttt{CSV} files will have noticed
that this method has many limitations: it is restricted to tabular data,
lacks type-safety, and has limited precision for numeric values.  Moreover,
ambiguities in the format itself frequently cause problems.  For example,
conventions on which characters is used as separator or decimal point vary by
country.  \emph{Extensible Markup Language} (\texttt{XML}) is another
well-established and widely-supported format with the ability to define just
about any arbitrarily complex schema \citep{nolan2013xml}. However, it pays
for this complexity with comparatively large and verbose messages, and added
complexity at the parsing side (which are somewhat mitigated by the
availability of mature libraries and parsers). Because \texttt{XML} is 
text-based and has no native notion of numeric types or arrays, it usually not a
very practical format to store numeric data sets as they appear in statistical
applications.

@@

This paper describes an \proglang{R} interface to Protocol Buffers,
and is organized as follows. Section~\ref{sec:protobuf}
provides a general high-level overview of Protocol Buffers as well as a basic
motivation for their use.
Section~\ref{sec:rprotobuf-basic} describes the interactive \proglang{R} interface
provided by the \CRANpkg{RProtoBuf} package, and introduces the two main abstractions:
\emph{Messages} and \emph{Descriptors}.  Section~\ref{sec:rprotobuf-classes}
details the implementation details of the main S4 classes and methods.  
Section~\ref{sec:types} describes the challenges of type coercion
between \proglang{R} and other languages.  Section~\ref{sec:evaluation} introduces a
general \proglang{R} language schema for serializing arbitrary \proglang{R} objects and evaluates
it against the serialization capabilities built directly into \proglang{R}.  Sections~\ref{sec:mapreduce}
and \ref{sec:opencpu} provide real-world use cases of \CRANpkg{RProtoBuf}
in MapReduce and web service environments, respectively, before
Section~\ref{sec:summary} concludes.

@@

\begin{itemize}
\item \emph{Portable}:  Enable users to send and receive data between
  applications as well as different computers or operating systems.
\item \emph{Efficient}:  Data is serialized into a compact binary
  representation for transmission or storage.
\item \emph{Extensible}:  New fields can be added to Protocol Buffer schemas
  in a forward-compatible way that does not break older applications.
\item \emph{Stable}:  Protocol Buffers have been in wide use for over a
  decade.
\end{itemize}

@@

Figure~\ref{fig:protobuf-distributed-usecase} illustrates an example
communication work flow with Protocol Buffers and an interactive \proglang{R} session.
Common use cases include populating a request remote-procedure call (RPC)
Protocol Buffer in \proglang{R} that is then serialized and sent over the network to a
remote server.  The server would then deserialize the message, act on the
request, and respond with a new Protocol Buffer over the network. 
The key difference to, say, a request to an \pkg{Rserve} instance is that
the remote server may be implemented in any language, with no
dependence on \proglang{R}.

@@

To illustrate how this method works, we attempt to convert all of the built-in 
data sets from \proglang{R} into this serialized Protocol Buffer representation.

@@

There are \Sexpr{n} standard data sets included in the \pkg{datasets}
package included with \proglang{R}. These data sets include data frames, matrices, time series, tables lists,
and some more exotic data classes. The \texttt{can\_serialize\_pb} method is 
used to determine which of those can fully be converted to the \texttt{rexp.proto}
Protocol Buffer representation. This method simply checks if any of the values or
attributes in an object is of an unsupported type:

@@

\Sexpr{m} data sets can be converted to Protocol Buffers
without loss of information (\Sexpr{format(100*m/n,digits=1)}\%). Upon closer
inspection, all other data sets are objects of class \texttt{nfnGroupedData}.
This class represents a special type of data frame that has some additional 
attributes (such as a \emph{formula} object) used by the \pkg{nlme} package.
Because formulas are \proglang{R} \emph{language} objects, they have little meaning to
other systems, and are not supported by the \texttt{rexp.proto} descriptor.
When \texttt{serialize\_pb} is used on objects of this class, it will serialize
the data frame and all attributes, except for the formula.

@@

Table~\ref{tab:compression} shows the sizes of 50 sample \proglang{R} data sets as
returned by object.size() compared to the serialized sizes.
%The summary compression sizes are listed below, and a full table for a
%sample of 50 data sets is included on the next page.  
Note that Protocol Buffer serialization results in slightly
smaller byte streams compared to native \proglang{R} serialization in most cases,
but this difference disappears if the results are compressed with gzip.
%Sizes are comparable but Protocol Buffers provide simple getters and setters
%in multiple languages instead of requiring other programs to parse the \proglang{R}
%serialization format. % \citep{serialization}.
One takeaway from this table is that the universal \proglang{R} object schema
included in \CRANpkg{RProtoBuf} does not in general provide
any significant saving in file size compared to the normal serialization
mechanism in \proglang{R}.
% redundant: which is seen as equally compact.
The benefits of \CRANpkg{RProtoBuf} accrue more naturally in applications where
multiple programming languages are involved, or when a more concise
application-specific schema has been defined.  The example in the next
section satisfies both of these conditions.

% latex table generated in \proglang{R} 3.0.2 by xtable 1.7-0 package
% Fri Dec 27 17:00:03 2013
\begin{table}[h!]
\begin{center}
  \small
\scalebox{0.9}{
\begin{tabular}{lrrrrr}
  \toprule
  Data Set & object.size & \multicolumn{2}{c}{\proglang{R} Serialization} &
  \multicolumn{2}{c}{RProtoBuf Serial.} \\
  & & default & gzipped & default & gzipped \\
  \cmidrule(r){2-6}
  uspop & 584 & 268 & 172 & 211 & 148 \\
  Titanic & 1960 & 633 & 257 & 481 & 249 \\
  volcano & 42656 & 42517 & 5226 & 42476 & 4232 \\
  euro.cross & 2728 & 1319 & 910 & 1207 & 891 \\
  attenu & 14568 & 8234 & 2165 & 7771 & 2336 \\
  ToothGrowth & 2568 & 1486 & 349 & 1239 & 391 \\
  lynx & 1344 & 1028 & 429 & 971 & 404 \\
  nottem & 2352 & 2036 & 627 & 1979 & 641 \\
  sleep & 2752 & 746 & 282 & 483 & 260 \\
  co2 & 4176 & 3860 & 1473 & 3803 & 1453 \\
  austres & 1144 & 828 & 439 & 771 & 410 \\
  ability.cov & 1944 & 716 & 357 & 589 & 341 \\
  EuStockMarkets & 60664 & 59785 & 21232 & 59674 & 19882 \\
  treering & 64272 & 63956 & 17647 & 63900 & 17758 \\
  freeny.x & 1944 & 1445 & 1311 & 1372 & 1289 \\
  Puromycin & 2088 & 813 & 306 & 620 & 320 \\
  warpbreaks & 2768 & 1231 & 310 & 811 & 343 \\
  BOD & 1088 & 334 & 182 & 226 & 168 \\
  sunspots & 22992 & 22676 & 6482 & 22620 & 6742 \\
  beaver2 & 4184 & 3423 & 751 & 3468 & 840 \\
  anscombe & 2424 & 991 & 375 & 884 & 352 \\
  esoph & 5624 & 3111 & 548 & 2240 & 665 \\
  PlantGrowth & 1680 & 646 & 303 & 459 & 314 \\
  infert & 15848 & 14328 & 1172 & 13197 & 1404 \\
  BJsales & 1632 & 1316 & 496 & 1259 & 465 \\
  stackloss & 1688 & 917 & 293 & 844 & 283 \\
  crimtab & 7936 & 4641 & 713 & 1655 & 576 \\
  LifeCycleSavings & 6048 & 3014 & 1420 & 2825 & 1407 \\
  Harman74.cor & 9144 & 6056 & 2045 & 5861 & 2070 \\
  nhtemp & 912 & 596 & 240 & 539 & 223 \\
  faithful & 5136 & 4543 & 1339 & 4936 & 1776 \\
  freeny & 5296 & 2465 & 1518 & 2271 & 1507 \\
  discoveries & 1232 & 916 & 199 & 859 & 180 \\
  state.x77 & 7168 & 4251 & 1754 & 4068 & 1756 \\
  pressure & 1096 & 498 & 277 & 427 & 273 \\
  fdeaths & 1008 & 692 & 291 & 635 & 272 \\
  euro & 976 & 264 & 186 & 202 & 161 \\
  LakeHuron & 1216 & 900 & 420 & 843 & 404 \\
  mtcars & 6736 & 3798 & 1204 & 3633 & 1206 \\
  precip & 4992 & 1793 & 813 & 1615 & 815 \\
  state.area & 440 & 422 & 246 & 405 & 235 \\
  attitude & 3024 & 1990 & 544 & 1920 & 561 \\
  randu & 10496 & 9794 & 8859 & 10441 & 9558 \\
  state.name & 3088 & 844 & 408 & 724 & 415 \\
  airquality & 5496 & 4551 & 1241 & 2874 & 1294 \\
  airmiles & 624 & 308 & 170 & 251 & 148 \\
  quakes & 33112 & 32246 & 9898 & 29063 & 11595 \\
  islands & 3496 & 1232 & 563 & 1098 & 561 \\
  OrchardSprays & 3600 & 2164 & 445 & 1897 & 483 \\
  WWWusage & 1232 & 916 & 274 & 859 & 251 \\
  \bottomrule
%  Total & 391176 & 327537 & 99161 & 313456 & 100308 \\
  Relative Size & 100\% & 83.7\% & 25.3\% & 80.1\% & 25.6\%\\
  \bottomrule
\end{tabular}
}
\caption{Serialization sizes for default serialization in \proglang{R} and
  \CRANpkg{RProtoBuf} for 50 \proglang{R} data sets.}
\label{tab:compression}
\end{center}
\end{table}

@@

The \texttt{HTTP GET} method is used to read a resource from OpenCPU. For example,
to access the data set \texttt{Animals} from the package \texttt{MASS}, a 
client performs the following HTTP request:

@@

Because both HTTP and Protocol Buffers have libraries available for many 
languages, clients can be implemented in just a few lines of code. Below
is example code for both \proglang{R} and Python that retrieves a data set from \proglang{R} with 
OpenCPU using a protobuf message. In \proglang{R}, we use the HTTP client from 
the \texttt{httr} package \citep{httr}. In this example we
download a data set which is part of the base \proglang{R} distribution, so we can
verify that the object was transferred without loss of information.

@@

This code suggests a method for exchanging objects between \proglang{R} servers, however this might as 
well be done without Protocol Buffers. The main advantage of using an inter-operable format 
is that we can actually access \proglang{R} objects from within another
programming language. For example, in a very similar fashion we can retrieve the same
data set in a Python client. To parse messages in Python, we first compile the 
\texttt{rexp.proto} descriptor into a python module using the \texttt{protoc} compiler:

@@

# Parse rexp.proto message
msg = REXP()
msg.ParseFromString(res.read())
print(msg)
\end{verbatim}
The \texttt{msg} object contains all data from the Animals data set. From here we
can easily extract the desired fields for further use in Python.

@@

\section{Summary}  
\label{sec:summary}
Over the past decade, many formats for interoperable
data exchange have become available, each with their unique features,
strengths and weaknesses.  
Text based formats such as \texttt{CSV} and \texttt{JSON} are easy to use, and will likely 
remain popular among statisticians for many years to come. However, in the 
context of increasingly complex analysis stacks and applications involving 
distributed computing as well as mixed language analysis pipelines, choosing a more 
sophisticated data interchange format may reap considerable benefits. 
%Protocol Buffers is itself not a protocol.
%Forward-compatibility is one of the features. No need to re-iterate those 
The Protocol Buffers standard and library offer a unique combination of features, 
performance, and maturity, that seems particularly well suited for data-driven 
applications and numerical computing.
